\documentclass[11pt,fleqn]{article}
\usepackage{latexsym}
\usepackage{amsmath,amsthm}

\begin{document}
\newcommand{\mbf}[1]{\mbox{{\bfseries #1}}}
\newcommand{\N}{\mbf{N}}
\renewcommand{\O}{\mbf{O}}
\newcommand{\tabfrac}[2]{%
	\setlength{\fboxrule}{0pt}%
	\fbox{$\frac{#1}{#2}$}%
}

\noindent Bill Davis 

\noindent October 22nd 2009 

\noindent Homework 7

\begin{enumerate}
 
\item[6.2.1]
\begin{enumerate}
  \item If the z score is less then -1.40507 then we should reject $H_0$. In
  this case 
  \[
  \displaystyle\frac{45.1-42.9}{\frac{3.2}{\sqrt{16}}} = -1.6667
  \]
  Where $P(Z<-1.667) = 0.04778$. We should then reject $H_0$ in favor of $H_1$.
  
    \item If the z score is outside of  -2.57583 then we should reject
    $H_0$. In this case 
  \[
  \displaystyle\frac{114-120}{\frac{18}{\sqrt{25}}} = 2.75
  \]
  Where $P(Z<2.75) = 0.99702$. We should then reject $H_0$ in favor of $H_1$.
  
      \item If the z score is greater then 1.12639 then we should reject $H_0$.
      In this case 
  \[
  \displaystyle\frac{15.8-14.2}{\frac{4.1}{\sqrt{9}}} = 1.1707
  \]
  Where $P(Z<1.1707) = 0.8791$. We should then reject $H_0$ in favor of $H_1$.
\end{enumerate}
\item[6.2.2]
Here Z values outside of +-1.88079 would cause $H_0$ to be rejected. In this
case 
\[
\frac{X-95}{\frac{15}{\sqrt{22}}} < -1.88079
\]
Then $X<88.9852$ or $X>101.015$ causes $H_0$ to be rejected.

\item[6.2.5]
No, it will not neccessarily be rejected because a two sided parameter it more
stringent then a single sided parameter. 

\item[6.2.7]
\begin{enumerate}
  \item
  For this sample the average is 12.75666667. Assuming 0.4
two-sided confidence interval the average means we should reject if the z score is outside of
+-1.95996.
\[
\frac{12.7566-12.6}{\frac{0.4}{\sqrt{30}}} < 2.1443
\]
Since the probabality that $P(X>2.1443) = 0.0160044 $ we should reject $H_0$
and have the machine be readjusted.
\item
Their is an assumption that the data is normally distributed around the mean,
it in fact does not have the characterstics of a normal distribution, this can
be seen from a histogram of the data. 
\end{enumerate} 
\item[6.3.1]
(a) We can compute the Z score for this test
\[
\frac{24-52(0.40)}{\sqrt{52(0.4)(0.6)}} = 0.905822
\]
Since this is less the the required Z score of  1.64, $H_0$ is not rejected. It
cannot be argued that the sound is any more effective for clearing fishing
waters. 

(b) 
The Z score 0.905822 corresponds to a P-value of 0.817485, which means that any
$\alpha$ value above 0.19 would cause the rejection of $H_0$
\item[6.3.3]
  The score can be computed as 
  \[
  \frac{72-0.65(120)}{\sqrt{120(0.65)(0.35)}} = -1.14834
  \]
  Where the one-sided 0.05 level of significance is -1.64485. Therefor thee
  null hypothesis is not rejected. 
\end{enumerate}

\end{document}