 \documentclass{article}
\usepackage{tikz}
\usepackage{skak} 
\usetikzlibrary{arrows,automata}
\usetikzlibrary{positioning}

\pagestyle{empty}

\begin{document}
Bill Davis\\
Homework 7

\begin{enumerate}

\item[5.1.1]
\begin{enumerate}  
    \item (5)(4) = 20
    \item (8)(7) = 56
\end{enumerate}

\item[5.1.5]
There are $26^4$ four letter words. And $\frac{26!}{22!}$ words without repetition.

\item[5.1.9]
\begin{enumerate}
\item (4 aces)(47 none queens - 1 ace) = 188
\item (1 queen of spades)(48) + (12 other spades)(47) = 612
\end{enumerate}

\item[5.1.18]
\begin{enumerate}
\item 
$(26^3)(10^3) + (10^3)(26^3) = 35152000$
\item
\[
\sum_{x=1}^{26}\sum_{y=1}^{26} (x+1)(10^x)(26^y) = 78960960
\]

\end{enumerate}

\item[5.1.26]
There are 12 arrangments of 8 and 9 into the 4 available spots and 8 non-8/9 numbers. The total number then is $8^2(12)=768$ and the probabality is $\frac{768}{10000} = 0.0768$. 

\item[5.1.36]
Not sure about this one. 
\item[5.2.2]
\[
\frac{26!}{16!} = 19275223968000
\]

\item[5.2.4]
There are 10! ways to choose the seats for 10 peoples. And if boys and girls alternate seats there are (10)(5)(4)(4)(3)(3)(2)(2)(1)(1) = 28800 ways. 

\item[5.2.17]
\begin{enumerate}
\item
\[
{4 \choose 2}\left( {6 \choose 4} + {6 \choose 5} + {6 \choose 6}\right) + {4 \choose 3} {6 \choose 6} 
\]

\item
\[ 
{9 \choose 5} + {9 \choose 4}  + {9 \choose 3} 
\]

\item
Number of ways to choose 5 people from 10 - number where three specific peoples are choosen. Since this equals the number of ways to choose 2 people from the remaining 7, then this equals
\[
{10 \choose 5} - {7 \choose 2} 
\]
\end{enumerate}

\item[5.2.19]
There are 6 different ways to arrange the languages, and for each n books in a language it can be ordered n! ways, therefore the answer is 
\[
(6)(6!)(8!)(5!)
\]

\item[5.2.27]
Since ${11 \choose 4} = 330$ and ${12 \choose 4} = 495$ he must have 12 friends. 

\item[5.2.38]
This is the number of ways to choose 8 months from 12 times the number of ways to choose a day from 30. 
\[
\frac{(30^8){12 \choose 8}}{{360 \choose 8}} = \frac{7217100000000}{143771059536281} = 0.050198558898279
\]
\end{enumerate}

\end{document}
